Value Ordering, Discrepancies, and Restarts for Subgraph Algorithms

### 2018-08-12 paper/paper.tex
Mucking around

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-others.pdf}

@@

    \caption{Above, the cumulative number of instances solved over time, comparing our algorithm
    (both in its basic form, and with the improvements introduced in the remainder of the paper) to
    other solvers. Below, the same, looking only at satisfiable instances.}
    \label{figure:others}
\end{figure}

>>>>

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-others.pdf}

    \smallskip

@@

    \centering
    \includegraphics*{gen-graph-others-induced.pdf}

    \smallskip

    \centering
    \includegraphics*{gen-graph-others-induced-zoom.pdf}

    \caption{On the top two rows, the cumulative number of instances solved over time, comparing our algorithm
    (both in its basic form, and with the improvements introduced in the remainder of the paper) to
    other solvers. The second considers only satisfiable instances. On the bottom two rows, the same,
    for the induced subgraph isomorphism problem.}
    \label{figure:others}
\end{figure}
